Automating Verification of MPC Security

### 2023-06-08 popl24/minicat.tex
checkpoint

\begin{example}[Lambda-obliv]
  \label{example-lambda-obliv}

  \begin{verbatimtab}
v[0,0] := select(s[1,0], flip[1,0], flip[1,1] );
v[0,1] := flip[1,0]
\end{verbatimtab}

\begin{verbatimtab}
v[0,0] := select(s[1,0],select(flip[1,0], flip[1,0], flip[1,1]),flip[1,2])
\end{verbatimtab}
\end{example}

\begin{example}[Oblivious Transfer]
  \label{example-lambda-OT}

\begin{verbatimtab}
v[2, rd] := select[flip[2, d], H[r1], H[r0]];
v[1, e] := s[2, c] xor flip[2, d];
v[2, f0] := s[1, m0] xor select[v[1, e], H[r1], H[r0]];
v[2, f1] := s[1, m1] xor select[not v[1, e], H[r1], H[r0]];
v[2, mc] := (select[s[2, c], v[2, f1], v[2, f0]] xor v[2, rd])
\end{verbatimtab}
\end{example}

\begin{example}[Additive Secret Sharing]
    \label{example-lambda-he}
Another 
example of an MPC protocol is additive secret sharing, where $k$
parties split up their secrets into \emph{shares}, with the property
that all $k$ shares are required to reconstruct the secret and any
fewer reveals nothing. In $\fedcat$, we can use $\ttt{xor}$, again, to
generate shares. Here, party 1 generates 3 shares of the secret
$\sx{1}{1}$- one is given to party 2 through view $\vx{2}{s1}$, one is
given to party 3 through view $\vx{3}{s1}$, and party 1 keeps
$\fx{1}{s1}$ for itself:
\begin{verbatimtab}
v[2,s1] := flip[1,1] xor flip[1,s1] xor s[1,1];
v[3,s1] := flip[1,1];
\end{verbatimtab}
Note that $\vx{2}{s1}$ and $\vx{3}{s1}$ are both in uniform
random distributions.

Another property of $\ttt{xor}$ is that it is additively homomorphic,
while functioning as addition in the boolean algebra (i.e., the binary
field). That is, given:
\begin{mathpar}
  x_1\ \ttt{xor}\ y_1 = z_1

  x_2\ \ttt{xor}\ y_2 = z_2
\end{mathpar}
then we have:
$$
(x_1\ \ttt{xor}\ x_2)\ \ttt{xor}\ (y_1\ \ttt{xor}\ y_2) = z_1\ \ttt{xor}\ z_2
$$
Thus, we can obtain secret 3-party summation (xor) by continuing
the protocol begun above- parties 2 and 3 can share their secrets
in the same fashion:
\begin{verbatimtab}
v[1,s2] := flip[2,1] xor flip[2,s2] xor s[2,1];
v[3,s2] := flip[2,1];

v[1,s3] := flip[3,1] xor flip[3,s3] xor s[3,1];
v[2,s3] := flip[3,1];
\end{verbatimtab}
Then, assuming that party 0 is the ``public party'', each party sums
its own shares, and then the sum of sum of shares is revealed
in the output view $\vx{0}{output}$. By additive homomorphism of
$\ttt{xor}$, this output is the sum of the 3 secrets, but
the protocol reveals nothing to the adversary, even if one
(or even two, in fact) of $\{1,2,3\}$ are corrupt. 
\begin{verbatimtab}
v[0,ss1] := v[1,s2] xor v[1,s3] xor flip[1,s1];
v[0,ss2] := v[2,s1] xor v[2,s3] xor flip[2,s2];
v[0,ss3] := v[3,s1] xor v[3,s2] xor flip[3,s3];

v[0,output] := v[0,ss1] xor v[0,ss2] xor v[0,ss3]
\end{verbatimtab}

Because this protocol correctly implements 3-party addition in the
binary field, it can reveal information to the adversary. For example,
suppose that $1 \in C$, and $\sx{1}{1}$ is $1$, and after running the
protocol suppose that $\vx{0}{output}$ is 0. Then the adversary knows
that 2 and 3's secrets are either 1 and 0, or 0 and 1, with 50/50
probability, and definitely neither 0 and 0, nor 1 and 1. However, the
protocol does not reveal anything more through adversarial views than
what the output reveals.
\end{example}

>>>>

\begin{example}[$\lambda_{\mathrm{obliv}}$]
  \label{example-lambda-obliv}
  In \cite{XXX}, Figure 3, two examples are introduced that illustrate
  subtleties of probabilistic programming in
  $\lambda_{\mathrm{obliv}}$, a language for oblivious memory
  management. We consider their translations here where we
  assume $H = \{ 1 \}$ and $C = \{ 0 \}$. First, the following
  examples shows that reuse of coin flips can result in release of
  information, even though flips are chosen from a uniform
  distribution. This is because the adversary can deduce that
  $\secret{1}{s}$ is more likely to be 1 in case their views are the
  same value:
  \begin{verbatimtab}
    v[0,0] := select(s[1,s], flip[1,sx], flip[1,sy]);
    v[0,1] := flip[1,sx] \end{verbatimtab}
  In the next example, since the nested select is more likely to evaluate
  to $1$ than $0$, the adversary can deduce that $\secret{1}{s}$ is
  more likely to be 1 in case $\view{0}{0}$ is 1:
  \begin{verbatimtab}
  v[0,0] := select(s[1,s],select(flip[1,sx], flip[1,sx], flip[1,sy]),flip[1,z]) \end{verbatimtab}
  We note that these examples are considered ``bad'' in \cite{XXX} since there
  no information about honest secrets should be revealed to the adversary in
  their threat model. For this reason they disallow reuse of flips through a
  linear type discipline, which is a culprit in both of these examples. However,
  as we have shown in Example \ref{example-otp} the reuse of flips is useful in
  the modeling of symmetric key encryption, and generally we will not enforce
  the same linear type discipline on the use of flips.
\end{example}

\begin{example}[Oblivious Transfer]
  \label{example-lambda-OT}
  In \cite{XXX} a protocol for $\ttt{OT}$ is defined that we recreate as
  follows, where client 2 is the receiver and client 1 is the sender. Whereas
  in \cite{XXX} a trusted third party provides the sender and receiver with
  shared randomness, in our version both clients refer to the oracle $\ttt{H}$
  to obtain shared random values. 
\begin{verbatimtab}
  v[2, rd] := select(flip[2, d], H[r1], H[r0]);
  v[1, e] := s[2, c] xor flip[2, d];
  v[2, f0] := s[1, m0] xor select(v[1, e], H[r1], H[r0]);
  v[2, f1] := s[1, m1] xor select(not v[1, e], H[r1], H[r0]);
  v[2, mc] := select(s[2, c], v[2, f1], v[2, f0]) xor v[2, rd]
\end{verbatimtab}
Below we will discuss how to automatically verify security properties
of this protocol that correspond to the properties proven manually in
\cite{XXX}, and additionally how to automatically verify its passive
security in the simulator model. With respect to our language primitives,
we note that this protocol is probabilistically equivalent to the
following:
\begin{verbatimtab}  
  view[2, mc] := OT(s[2, c], s[1, m1], s[1, m0])
\end{verbatimtab}
\end{example}

\begin{example}[Additive Secret Sharing]
    \label{example-lambda-he}
Additive secret sharing is an MPC protocol where $k$ parties split up
their secrets into \emph{shares}, with the property that all $k$
shares are required to reconstruct the secret and any fewer reveals
nothing. Additionally, this sharing enjoys additive homomorphism. In
the binary field it is well-known that we can extend our use
of $\ttt{xor}$ and flips to generate an arbitrary number of shares
with additive homomorphism.

For example, to generate shares for three-party additive sharing,
clients 1,2, and 3 can break up and distribute their shares to
each other as follows:
\begin{verbatimtab}
  v[2,s1] := flip[1,1] xor flip[1,s1] xor s[1,1];
  v[3,s1] := flip[1,1];

  v[1,s2] := flip[2,1] xor flip[2,s2] xor s[2,1];
  v[3,s2] := flip[2,1];

  v[1,s3] := flip[3,1] xor flip[3,s3] xor s[3,1];
  v[2,s3] := flip[3,1];
\end{verbatimtab}
Then, assuming that party 0 is a ``public'' client, each party sums
its own shares, and then the sum of sum of shares is revealed
in the output view $\vx{0}{output}$. By additive homomorphism of
$\ttt{xor}$, this output is the sum of the 3 secrets.
\begin{verbatimtab}
  v[0,ss1] := v[1,s2] xor v[1,s3] xor flip[1,s1];
  v[0,ss2] := v[2,s1] xor v[2,s3] xor flip[2,s2];
  v[0,ss3] := v[3,s1] xor v[3,s2] xor flip[3,s3];

  v[0,output] := v[0,ss1] xor v[0,ss2] xor v[0,ss3]
\end{verbatimtab}
We note that, as for MPC protocols generally, the notion of
``secrecy'' here is subtle and not the same as for encryption as in
Example \ref{example-otp}, particularly when the threat model allows
protocol participants to be corrupt. For example, suppose that $1 \in C$, and
$\sx{1}{1}$ is $1$, and after running the protocol suppose that
$\vx{0}{output}$ is 0. Then the adversary knows that 2 and 3's secrets
are either 1 and 0, or 0 and 1, with 50/50 probability, and definitely
neither 0 and 0, nor 1 and 1. 
\end{example}
